Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-10-06 04_paper/1006_draft.Rmd
building on aid section

The secrecy surrounding China's international development financing is puzzling. But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending. **They find** that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors **(citation needed)**. Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics. These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.

@@

# Motivations behind Chinese Foreign Aid

@@

# Media’s Agenda-Setting Effects

@@

Hence, while Xinhua plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of Xinhua to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.

@@

Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country. For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people – and listen to them" [@hoffman_introduction_1968, p. 4]. In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" [@deibel_culture_1976, p. 15].

@@

We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion. News editors build the credibility of the news agency to transmit information around the globe. High-level officials spend time and resources to visit other countries for economic or security purposes – to strengthen the bilateral relationship. Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically. In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing. They are in the potential friend circle. While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic. Foreign aid, instead, provides tangible and materials support to the countries in need. Hence, we expect China to prioritize giving foreign aid to its “friends” -- countries where China has developed multi-facet relationships through public diplomacy efforts. This rationale leads to our hypotheses:

>>>>

The secrecy surrounding China's international development financing is puzzling. But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending. In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors. Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics. These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.

@@

# Motivations behind Chinese Overseas Financing

@@

In addition to considering how diplomatic missions and state-sponsored outward-facing media correspond with Beijing's development finance, we also distinguish between Beijing's ODA-like expenditures and its other official flows (OOF). The former we may call aid (or development assistance), and the latter we may call debt (or loans). As @dreher_banking_2022 note, Beijing uses aid and debt to accomplish different goals, and it further does not finance them in equal proportion, both in terms of total spending and in terms of how it targets funds across developing countries. @dreher_banking_2022 argue that aid tends to be most associated with China's foreign policy goals, while debt tends to correspond to its market interests. What do these differences imply for Beijing's bilateral diplomacy and state-sponsored foreign media?

On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences. On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic. Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy. On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically. As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources. When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans[@dreher_banking_2022].

# Media's Agenda-Setting Effects

@@

Hence, while Xinhua plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of Xinhua to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.

@@

Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country. For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" [@hoffman_introduction_1968, p. 4]. In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" [@deibel_culture_1976, p. 15].

@@

We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion. News editors build the credibility of the news agency to transmit information around the globe. High-level officials spend time and resources to visit other countries for economic or security purposes -- to strengthen the bilateral relationship. Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically. In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing. They are in the potential friend circle. While public diplomacy is one way to increase a state's soft power, in the end, it is intangible power and symbolic. Foreign aid, instead, provides tangible and materials support to the countries in need. Hence, we expect China to prioritize giving foreign aid to its "friends" -- countries where China has developed multi-facet relationships through public diplomacy efforts. This rationale leads to our hypotheses:
